Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
cosmetic change to rescure highlighting of Emacs.
outline of Conclusion.

\begin{quote}\small\begin{verbatim}
assertRaises :: (Show a, Exception e, Show e, Eq e) =>
  String -> e -> IO a -> IO ()
\end{verbatim}\end{quote}
        But it has several shortcomings:
        \begin{itemize}
            \item
                It only works for exceptions with an {\tt Eq}
                instance, but several standard exceptions (most
                prominently {\tt ErrorCall}) have no {\tt Eq}
                instance.
            \item
                It places an unnecessary {\tt Show} constraint on the
                result of the {\tt IO} action, further limiting it's
                applicability.
            \item
                It only allows to expect specific values; expecting
                any exception of a certain type is not possible.
        \end{itemize}
\end{itemize}

@@

\begin{quote}
    TBD

    sol: @kazu, can you work on this, if you have time.  I think an
    ``itemized'' list is better than text.  It's more flexible for
    now, and @mkl or @sol can do the final wording)
\end{quote}

>>>>

\begin{quote}
\small
\begin{verbatim}
assertRaises :: (Show a, Exception e, Show e, Eq e) =>
  String -> e -> IO a -> IO ()
\end{verbatim}\end{quote}
        But it has several shortcomings:
        \begin{itemize}
            \item
                It only works for exceptions with an {\tt Eq}
                instance, but several standard exceptions (most
                prominently {\tt ErrorCall}) have no {\tt Eq}
                instance.
            \item
                It places an unnecessary {\tt Show} constraint on the
                result of the {\tt IO} action, further limiting it's
                applicability.
            \item
                It only allows to expect specific values; expecting
                any exception of a certain type is not possible.
        \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item We discussed how to carry out BDD in Haskell.
\item We proposed to use Doctest for user documentation
and Hspec for code documentation.
\item We enhanced Haddock to support examples and properties, 
and implemented Doctest integrated with QuickCheck.
\item We also supplied expectation combinators to Hspec.
\item With these two tools, specification can also be used for
documentation and automatic testing.
\item test discovery
\item This enhances the value of test code and would motivate
Haskell programmers to write test code.
\end{itemize}
